Rates and delay times of type Ia supernovae in the Dark Energy Survey

### 2021-06-21 ref_response.tex
Updates from Overleaf

An alternative view on how the SN Ia rate relates to environment can be gained by calculating the rate of SNe per year per unit stellar mass: SNuM. A measurement of the SNuM is achieved by summing the number of SNe in each stellar mass bin, and dividing by the total stellar mass of field galaxies in that bin. We show the SNuM as a function of galaxy stellar mass in Fig.~ \ref{fig:snum}, along with the measurements from SNe discovered in SDSS spectra \citep{Graur2013} at $z\sim0.1$ and at $z\sim0$ in LOSS as presented in \citet{Li2011a}. We also calculate the SNuM predicuted by our model for each simulated galaxy at a range of redshifts and plot these as curves in Fig.~\ref{fig:snum}. Our model accurately recovers the SNuM measured in DES for the redshift and stellar mass range of the data. While the data from LOSS and SDSS spectra lie slightly higher than our model prediction, the difference is consistent with differences in assumed SFHs, IMFs and stellar population templates as well as SN detection method. Any true residual difference between predicted and observed SNuM at different redshifts could be caused by an evolution of the SN Ia production efficiency as a function of redshift; we defer such an investigation to future work with more refined models and measurements.
\section{The delay-time distribution as a function of supernova properties}
\label{sec:split_x1_c}

>>>>

An alternative view on how the SN Ia rate relates to environment can be gained by calculating the rate of SNe per year per unit stellar mass: SNuM. A measurement of the SNuM is achieved by summing the number of SNe in each stellar mass bin, and dividing by the total stellar mass of field galaxies in that bin. We show the SNuM as a function of galaxy stellar mass in Fig.~ \ref{fig:snum}, along with the measurements from SNe discovered in SDSS spectra \citep{Graur2013} at $z\sim0.1$ and at $z\sim0$ in LOSS as presented in \citet{Li2011a}. We also calculate the SNuM predicuted by our model for each simulated galaxy at a range of redshifts and plot these as curves in Fig.~\ref{fig:snum}. Our model accurately recovers the SNuM measured in DES for the redshift and stellar mass range of the data. While the data from LOSS and SDSS spectra lie slightly higher than our model prediction, the difference is consistent with differences in assumed SFHs, IMFs and stellar population templates as well as SN detection method. Any true residual difference between predicted and observed SNuM at different redshifts could be caused by an evolution of the SN Ia production efficiency as a function of redshift; we defer such an investigation to future work with more refined models and measurements.

There is tentative evidence in the data for a flattening of the SNum vs stellar mass at $\log(M/\mathrm{M}_{\odot})\leq9.5$, which is broadly predicted by the model and is qualitatively consistent with the shape of the analytic fit of \citet{Kistler2013} while standing in slight tension with the conclusions of \citet{Brown2019}. The uncertainty of the measured rates at these low stellar masses prevents us from drawing further conclusions at this stage.
\section{The delay-time distribution as a function of supernova properties}
\label{sec:split_x1_c}
